---
title: "Workflow AFU"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  pdf_document:
    toc: yes
editor_options:
  markdown:
    wrap: 75
---

Course: Field Course Micrometeorology and Urban Climate at the University
of Bern (Institute of Geography)

Supervisor: Prof. Dr. Stefan Brönnimann

Adviser: Dr. Moritz Gubler

[Do you have questions about the workflow? Contact the
Authors:]{.underline}

Bigler Patrick
([patrick.bigler1\@students.unibe.ch](mailto:patrick.bigler1@students.unibe.ch){.email})

Sarah Ogi (sarah.ogi\@students.unibe.ch)

Markella Bouchoriku (markella.bouchoriku\@students.unibe.ch )

Reference: Amt für Umwelt (AFU)

# Introduction

|              |                                         |
|--------------|-----------------------------------------|
| Coordinates: | 7° 27' 45,252'' E ; 46.° 57' 47,196'' N |
| Altitude:    | 554.5 a.s.l.                            |
| Time:        | UTC-2 / GMT-2                           |
| Source:      | AFU (Amt für Umwelt der Stadt Bern)     |

: Table 1: Metadata for the MeteoSchweiz station in Zollikofen (reference
station)

+-----------------+--------------------------------------------+
| Altitude:       | 7° 27' 45,252'' E ; 46.° 57' 47,196'' N    |
+-----------------+--------------------------------------------+
| Altitude:       | 554.5 a.s.l.                               |
+-----------------+--------------------------------------------+
| Time format:    | Old logger: UTC-2 / GMT-2                  |
|                 |                                            |
|                 | New Logger: UTC / GMT                      |
+-----------------+--------------------------------------------+
| Logger Number:  | 83                                         |
+-----------------+--------------------------------------------+
| Code grafana    | d6e2769def35                               |
+-----------------+--------------------------------------------+

: Table 2: Metadata for the 2m Logger at AFU

# Preparation

First, we install and / or load packages we need. Important is the package
"conflicted". It enables us to chose if different functions have the same
call but do not make the same thing (a function in a certain package can
have the same name as a function from another package).

```{r read_the_packages, warning=FALSE, error=FALSE, message=FALSE}
# install and activate all packages we need
source("../R/general/packages.R")

# We set preferences
conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::rename)
conflicts_prefer(Metrics::rmse)
conflicts_prefer(Metrics::mae)
conflicts_prefer(lubridate::stamp)
conflicts_prefer(lubridate::hour)
conflicts_prefer(recipes::fixed)
```

We read all the data we need:

```{r read_the_files, warning=FALSE, error=FALSE, message=FALSE}
# We read a file with data from the old loggers
old_logger <- read_xlsx("../data/data_logger_old.xlsx")

# We read data from the new logger in front of AFU (2m)
new_logger_AFU <- read.csv("../data/data_logger_new/d6e2769def35.csv")

# We read data from the station in front of AFU (2m)
AFU_ref <- read_xlsx("../data/data_REF_AFU_new.xlsx")
```

# Data quality

Now we need a first impression about the data. Are there any missing values
and if yes, where are they?

## Missing Values

```{r handle_missing_values,  warning=FALSE, error=FALSE, message=FALSE}
# Load the function to handle NAs
source("../R/general/function.visualize.na.values.R")

# We check the dataquality of the reference station
visualize.na.values.without.groups(AFU_ref)

# We check the dataquality of the new loggers
visualize.na.values.without.groups(new_logger_AFU)

# We check the dataquality of the old loggers
visualize.na.values.without.groups(old_logger)
```

## Time-shift

Because not all data has the same source we have to make sure all data
works in the same time zone. For that we use lubridate which gives all the
data a proper time- and date stamp. The old loggers works with CEST
(Central Europe Summer Time). We define this time zone for the loggers
(CEST = GMT -2). We do the same for the reference station due to the same
reasons as for the old loggers. The new loggers works on UTC and therefore,
we define it as GMT. If we defined time zones, R will do the corrections
automatically.

Further, it is easier to work with one data frame. That is why me join all
three data frames into one. We make sure that we only use data if the date
and time occur in all three data frames. For that, we round the time to the
next 10 minutes.

```{r time_shift, error=FALSE, message=FALSE, warning=FALSE}
#First, change format of time and date for the old logger in front of AFU
old_logger$Sommerzeit <- strptime(old_logger$Sommerzeit, format="%Y-%m-%d %H:%M")
old_logger$Sommerzeit <- as.POSIXct(old_logger$Sommerzeit, tz = "Etc/GMT-2")
attr(old_logger$Sommerzeit, "tzone")
# We change a name of the column
old_logger <- old_logger|>
  rename('time' = Sommerzeit)

# We change format of time and date for reference station in front of AFU
AFU_ref$Zeit <- format(AFU_ref$Zeit, format = "%H:%M")
AFU_ref$Datum <- strptime(paste(AFU_ref$Datum,AFU_ref$Zeit,sep = " "), format="%Y-%m-%d %H:%M") 
AFU_ref$Datum <- as.POSIXct(AFU_ref$Datum, tz = "Etc/GMT-2")
attr(AFU_ref$Datum, "tzone")
# We change the class of the temperature column to numeric abd rename a column
AFU_ref <- AFU_ref|>
  mutate(temp_ref = as.numeric(Temp))|>
  rename('time' = Datum)

# We change format of time and date for the new logger in front of AFU
new_logger_AFU$time <- gsub('[TZ]',' ', new_logger_AFU$time)
new_logger_AFU$time <- strptime(new_logger_AFU$time, format = "%Y-%m-%d %H:%M")
new_logger_AFU$time <- as.POSIXct(new_logger_AFU$time, tz = "Etc/GMT")
attr(new_logger_AFU$time, "tzone")
# We round the time to the next 10 minute and rename a column
new_logger_AFU <- new_logger_AFU|>
  mutate(time = lubridate::round_date(time,"10 minutes"))|>
  rename('temp_new_logger' = decodedXpayload_temperature)

# We join two datasets
AFU_all_1 <- dplyr::inner_join(AFU_ref, new_logger_AFU, by = 'time')
# We join two datasets
AFU_all_2 <- dplyr::inner_join(AFU_all_1, old_logger, by = 'time')
# We change the class of a column ans select only columns we need
AFU_combined <- AFU_all_2|>
  mutate(temp_ref = as.numeric(Temp))|>
  select(c('time', 'temp_ref', 'Log_83', 'temp_new_logger'))|>
  rename(temp_old_logger = 'Log_83')|>
  mutate('Row' = c(1 : 4151))

# We make sure that every error appear as NA
AFU_combined[AFU_combined == -9999] <- NA
```

Because we want to be sure that the time shift worked we visualize 48h of
each data file.

```{r vis_time_shift_control, warning=FALSE, error=FALSE, message=FALSE}
# We plot 48h to be sure that the time shift worked
AFU_combined|>
  # We filter 48h
  filter(Row > 1402 & Row < 1688)|>
  # We create a new table
    pivot_longer(cols = c(temp_ref, temp_new_logger, temp_old_logger),
               names_to = "Legend",
               values_to = "values")|>
  # We create a ggplot - line plot
  ggplot(aes(x = time, y = values, color = Legend)) + 
  geom_line(linewidth = 0.3)+
  labs(x = 'Time', y = 'Absolute Temperature', title = 'AFU: Time shift control')+
  theme_light()
```

## Calculate anomalies

We are not interested in the absolute values but in the anomalies. Here, we
calculate those and add it to our data frame.

```{r calculate_anomalies, warning=FALSE, error=FALSE, message=FALSE}
AFU_combined <- AFU_combined|>
  mutate('Anomaly_new_log_ref' = temp_new_logger - temp_ref,
         'Anomaly_old_log_ref' = temp_old_logger - temp_ref,
         'Anomaly_new_log_old_log' = temp_new_logger - temp_old_logger)
```

## Suspected data

We want a "feeling" for our data. Are there outliers? If yes, why there? To
answer those questions we aggregate the 10 minute resolution to a 2 hour
resolution and plot them. We can see that most of the anamolies are in a
[-3, 3] °C range. But there also are outliers up to about 20°C. Maybe there
were a problem with the station.

We filter our data to determine those "extreme-outliers" because it does
not seems like a expected variability. In the data we see, that the
reference station seems to be broken down. The station repeatedly measures
the same value, followed by NAs. The station probably got stuck. The second
peak is about 5-6 °C. Because this event occurred only 2 hours after the
station failure, we assume that this was also due to problems with the
measuring station. Therefore, we exclude this part of the data from our
analysis.

```{r suspected_data, warning=FALSE, error=FALSE, message=FALSE}
# We create a column-plot of the anomalies. 
AFU_combined|>
  mutate(aggregate_hourly = lubridate::round_date(time, "2 hours"))|>
  group_by(aggregate_hourly)|>
  mutate(daily = lubridate::day(time))|>
  # We create a new table
  pivot_longer(cols = c(`Anomaly_new_log_ref`, 
                        `Anomaly_old_log_ref`, 
                        `Anomaly_new_log_old_log`),
                         names_to = "Legend",
                         values_to = "values")|>
  ggplot(aes(x = daily, y = values, color = Legend))+
  geom_col(position="dodge", stat="identity")+
    guides(size = FALSE) + 
  theme(plot.margin = margin(2,.8,2,.8, "cm"),
        plot.background = element_rect(fill = "darkgrey"))+
  theme_light()

# We filter the data for all values > 3 °C --> check the rows!
AFU_combined|>
  filter(`Anomaly_new_log_ref` > 3 | 
           `Anomaly_old_log_ref` > 3 | 
           `Anomaly_new_log_old_log` > 3 )

# We filter the dataset by rows and exclude some data
# Row numbers 3316 - 3489 (7.6.23, 7:00 - 8.6.23, 12:00)
# Row numbers 3513 - 3525 (8.6.23, 16:00 - 8.6.23, 18:00)
AFU_combined|>
  filter(! Row %in% c(3316:3489, 3513:3525))|>
    mutate(aggregate_hourly = lubridate::round_date(time, "2 hours"))|>
  group_by(aggregate_hourly)|>
  mutate(daily = lubridate::day(time))|>
  # We create a new table
  pivot_longer(cols = c(`Anomaly_new_log_ref`, 
                        `Anomaly_old_log_ref`, 
                        `Anomaly_new_log_old_log`),
                         names_to = "Legend",
                         values_to = "values")|>
  ggplot(aes(x = daily, y = values, color = Legend))+
  geom_col(position="dodge", stat="identity")+
    guides(size = FALSE) + 
  theme(plot.margin = margin(2,.8,2,.8, "cm"),
        plot.background = element_rect(fill = "darkgrey"))+
  theme_light()

# We redefine the data and exclude the rows where the measuring station was broken.   
AFU_combined <- AFU_combined|>
  filter(! Row %in% c(3316:3489, 3513:3525))|>
  drop_na()


# We write it into a CSV file
# We want to know, if a certain file already exists
name.of.file <- "../data/AFU_combined.csv"

# If do not exists such a file, create it!
if (!file.exists(name.of.file)){
  # Convert the xlsx to a csv file
  write_csv(AFU_combined, "../data/AFU_combined.csv")

  # If exists such a file, we do nothing!
  }else{}
```

# Analysis

Now we are ready for the analysis. First, we write some dynamic functions
for the plots. After that, we use box-plot, density-plots and line-graphs
to visualize the performance of the loggers. After that, we calculate the
main statistic parameters and the errors. Because the problems are probably
higher due to solar radiation through the day, we differentiate between 24h
(whole day), 6-22 (day-time) and 22-6 (night-time).

## Data Split

```{r split_data }
AFU_day <- AFU_combined|>
  mutate(aggregate_hourly = lubridate::round_date(time, "60 minutes"))|>
  group_by(aggregate_hourly)|>
  mutate(hourly = lubridate::hour(aggregate_hourly))|>
  filter(hourly >= 6 & hourly <= 22)

AFU_night <- AFU_combined|>
  mutate(aggregate_hourly = lubridate::round_date(time, "60 minutes"))|>
  group_by(aggregate_hourly)|>
  mutate(hourly = lubridate::hour(aggregate_hourly))|>
  filter(hourly < 7 | hourly > 21)
```

## Functions

Here, we create function for the plots (line-plot, box-plot and
density-plot. We add ± standard deviation and a dot-dashed zero line
because we want to determine whether the data is accurate or and precise.

```{r function, warning=FALSE, error=FALSE, message=FALSE}
source("../R/general/plot.functions.R")
```

## Line-plot

Whole Day

```{r line_graph, warning=FALSE, error=FALSE, message=FALSE}
# Line-plot new logger - reference station at AFU
overview_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6)

# Line-plot old logger - reference station at AFU
overview_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7)

# line-plot new logger - old logger at AFU
overview_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8)

```

## Scatter-Plot

```{r scatter_plot}
# Scatter-plot new logger - reference station at AFU
overview_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6, whole = FALSE)
# scatterplot old logger - reference station at AFU
overview_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7, whole = FALSE)
# scatterplot new logger - old logger at AFU
overview_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8, whole = FALSE)
```

## Box-plot

```{r boxplot, warning=FALSE, error=FALSE, message=FALSE}
# Boxplot new logger - reference station at AFU
boxplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6)

# Boxplot old logger - reference station at AFU
boxplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7)

# Boxplot new logger - old logger at AFU
boxplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8)
```

Day-time

```{r boxplot_day}
# Boxplot new logger - reference station at AFU (daytime)
boxplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6, whole = FALSE)

# Boxplot old logger - reference station at AFU (daytime)
boxplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7, whole = FALSE)

# Boxplot new logger - old logger at AFU (daytime)
boxplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8, whole = FALSE)
```

Night-time

```{r boxplot_night}
# Boxplot new logger - reference station at AFU (nighttime)
boxplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6, whole = FALSE, day = FALSE)

# Boxplot old logger - reference station at AFU (nighttime)
boxplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7, whole = FALSE, day = FALSE)

# Boxplot new logger - old logger at AFU (nighttime)
boxplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8, whole = FALSE, day = FALSE)
```

## Density-plot

Whole day

```{r density-plot, warning=FALSE, error=FALSE, message=FALSE}

# Densityplot new logger - reference station at AFU
densityplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6)

# Densityplot old logger - reference station at AFU
densityplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7)

# Densityplot new logger - old logger at AFU
densityplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8)
```

Day-time

```{r density_day}
# Densityplot new logger - reference station at AFU (daytime)
densityplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6, whole = FALSE)

# Densityplot old logger - reference station at AFU (daytime)
densityplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7, whole = FALSE)

# Densityplot new logger - old logger at AFU (daytime)
densityplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8, whole = FALSE)
```

Night-time

```{r density_night}
# Densityplot new logger - reference station at AFU (nighttime)
densityplot_creater(AFU_combined, Anomaly_new_log_ref, colnbr = 6, whole = FALSE, day = FALSE)

# Densityplot old logger - reference station at AFU (nighttime)
densityplot_creater(AFU_combined, Anomaly_old_log_ref, colnbr = 7, whole = FALSE, day = FALSE)

# Densityplot new logger - old logger at AFU (nighttime)
densityplot_creater(AFU_combined, Anomaly_new_log_old_log, colnbr = 8, whole = FALSE, day = FALSE)
```

# Statistics

## Errors

```{r errors}
NAMES <- c('24h, new-ref', '24h, old-ref', 
           'day-time, new-ref', 'day-time, old-ref', 
           'night-time, new-ref', 'night-time, old-ref',
           '24h, new-old', 'day-time, new-old', 'night-time, new-old')


RMSE <- c(round(sqrt(mean((AFU_combined$temp_new_logger-AFU_combined$temp_ref)^2, na.rm = TRUE)), 
                digits = 3),
          round(sqrt(mean((AFU_combined$temp_old_logger-AFU_combined$temp_ref)^2,na.rm = TRUE)), 
                digits = 3),
          round(sqrt(mean((AFU_day$temp_new_logger-AFU_day$temp_ref)^2,na.rm = TRUE)), digits = 3),
          round(sqrt(mean((AFU_day$temp_old_logger-AFU_day$temp_ref)^2,na.rm = TRUE)), digits = 3),
          round(sqrt(mean((AFU_night$temp_new_logger-AFU_night$temp_ref)^2,na.rm = TRUE)),digits = 3),
          round(sqrt(mean((AFU_night$temp_old_logger-AFU_night$temp_ref)^2,na.rm = TRUE)),digits = 3),
          round(sqrt(mean((AFU_combined$temp_new_logger-AFU_combined$temp_old_logger)^2,na.rm = TRUE)), digits = 3),
          round(sqrt(mean((AFU_day$temp_new_logger-AFU_day$temp_old_logger)^2,na.rm = TRUE)),digits = 3),
          round(sqrt(mean((AFU_night$temp_new_logger-AFU_night$temp_old_logger)^2,na.rm = TRUE)),digits = 3))


MAE <- c(round(mean(abs(AFU_combined$temp_new_logger-AFU_combined$temp_ref),na.rm = TRUE), digits = 3),
         round(mean(abs(AFU_combined$temp_old_logger-AFU_combined$temp_ref),na.rm = TRUE), digits = 3),
         round(mean(abs(AFU_day$temp_new_logger-AFU_day$temp_ref), na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_day$temp_old_logger-AFU_day$temp_ref), na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_night$temp_new_logger-AFU_night$temp_ref), na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_night$temp_old_logger-AFU_night$temp_ref), na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_combined$temp_new_logger-AFU_combined$temp_old_logger),na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_day$temp_new_logger-AFU_day$temp_old_logger), na.rm = TRUE),digits = 3),
         round(mean(abs(AFU_night$temp_new_logger-AFU_night$temp_old_logger), na.rm = TRUE),digits = 3))

BIAS <- c(round((sum(AFU_combined$temp_new_logger-AFU_combined$temp_ref, na.rm = TRUE)/
                   length(AFU_combined$temp_ref)), digits = 3), 
          round((sum(AFU_combined$temp_old_logger - AFU_combined$temp_ref, na.rm = TRUE)/
                   length(AFU_combined$temp_ref)), digits = 3),
          round((sum(AFU_day$temp_new_logger - AFU_day$temp_ref, na.rm = TRUE)/
                   length(AFU_day$temp_ref)), digits = 3), 
          round((sum(AFU_day$temp_old_logger - AFU_day$temp_ref, na.rm = TRUE)/
                   length(AFU_day$temp_ref)), digits = 3),
          round((sum(AFU_night$temp_new_logger - AFU_night$temp_ref, na.rm = TRUE)/
                   length(AFU_night$temp_ref)), digits = 3), 
          round((sum(AFU_night$temp_old_logger - AFU_night$temp_ref, na.rm = TRUE)/
                   length(AFU_night$temp_ref)), digits = 3),
          round((sum(AFU_combined$temp_new_logger - AFU_combined$temp_old_logger, na.rm = TRUE)/
                   length(AFU_combined$temp_ref)), digits = 3),
          round((sum(AFU_day$temp_new_logger - AFU_day$temp_old_logger, na.rm = TRUE)/
                   length(AFU_day$temp_old_logger)), digits = 3),
          round((sum(AFU_night$temp_new_logger - AFU_night$temp_old_logger, na.rm = TRUE)/
                   length(AFU_night$temp_old_logger)), digits = 3))

test <- cbind(NAMES, RMSE, MAE, BIAS)
knitr::kable(test, caption = 'Table 1: Overview about error-metrics')|>
    kableExtra::kable_classic_2(full_width = T)
  
```

## Main Parameters

```{r statistics}
# Calculate the main statistic parameters
knitr::kable(AFU_combined|>
  rename(new_ref = `Anomaly_new_log_ref`,
         old_ref = `Anomaly_old_log_ref`,
         new_old = `Anomaly_new_log_old_log`)|>
  mutate(aggregate_hourly = lubridate::round_date(time, "60 minutes"))|>
  group_by(aggregate_hourly)|>
  mutate(hourly = lubridate::hour(aggregate_hourly))|>
  pivot_longer(cols = c(`new_ref`, 
                        `old_ref`, 
                        `new_old`),
                         names_to = "Device",
                         values_to = "values")|>
  select('Device', 'values')|>
  group_by(Device)|>
  dplyr::summarise(mean = round(mean(values, na.rm = TRUE), digits = 3),
         median = round(median(values, na.rm = TRUE), digits = 3),
         max = round(max(values, na.rm = TRUE), digits = 3),
         min = round(min(values, na.rm = TRUE), digits = 3),
         std = round(sd(values, na.rm = TRUE), digits = 3),
         q25 = round(quantile(values, probs = .25,na.rm = TRUE), digits = 3),
         q75 = round(quantile(values, probs = .75,na.rm = TRUE), digits = 3),
         iqr = round(IQR(values,na.rm = TRUE), digits = 3),
         spread = round(max(values, na.rm = TRUE)-min(values, na.rm = TRUE), digits = 3),
         skewness = round(skewness(values, na.rm = TRUE), digits = 3)),
  caption = "Table 2: Main statistics parameters of AFU (whole day)",
  align = c('l', rep('c', times = 10)))|>
  kableExtra::kable_classic_2(full_width = T)

knitr::kable(AFU_combined|>
  rename(new_ref = `Anomaly_new_log_ref`,
         old_ref = `Anomaly_old_log_ref`,
         new_old = `Anomaly_new_log_old_log`)|>
  mutate(aggregate_hourly = lubridate::round_date(time, "60 minutes"))|>
  group_by(aggregate_hourly)|>
  mutate(hourly = lubridate::hour(aggregate_hourly))|>
  filter(hourly >= 6 & hourly <= 22)|>
  pivot_longer(cols = c(`new_ref`, 
                        `old_ref`, 
                        `new_old`),
                         names_to = "Device",
                         values_to = "values")|>
  select('Device', 'values')|>
  group_by(Device)|>
  dplyr::summarise(mean = round(mean(values, na.rm = TRUE), digits = 3),
         median = round(median(values, na.rm = TRUE), digits = 3),
         max = round(max(values, na.rm = TRUE), digits = 3),
         min = round(min(values, na.rm = TRUE), digits = 3),
         std = round(sd(values, na.rm = TRUE), digits = 3),
         q25 = round(quantile(values, probs = .25,na.rm = TRUE), digits = 3),
         q75 = round(quantile(values, probs = .75,na.rm = TRUE), digits = 3),
         iqr = round(IQR(values,na.rm = TRUE), digits = 3),
         spread = round(max(values, na.rm = TRUE)-min(values, na.rm = TRUE), digits = 3),
         skewness = round(skewness(values, na.rm = TRUE), digits = 3)),
  caption = "Table 3: Main statistics parameters of AFU (night-time)", 
  align = c('l', rep('c', times = 10)))|>
  kableExtra::kable_classic_2(full_width = T)

knitr::kable(AFU_combined|>
  rename(new_ref = `Anomaly_new_log_ref`,
         old_ref = `Anomaly_old_log_ref`,
         new_old = `Anomaly_new_log_old_log`)|>
  mutate(aggregate_hourly = lubridate::round_date(time, "60 minutes"))|>
  group_by(aggregate_hourly)|>
  mutate(hourly = lubridate::hour(aggregate_hourly))|>
  filter(hourly < 7 | hourly > 21)|>
  pivot_longer(cols = c(`new_ref`, 
                        `old_ref`, 
                        `new_old`),
                         names_to = "Device",
                         values_to = "values")|>
  select('Device', 'values')|>
  group_by(Device)|>
  dplyr::summarise(mean = round(mean(values, na.rm = TRUE), digits = 3),
         median = round(median(values, na.rm = TRUE), digits = 3),
         max = round(max(values, na.rm = TRUE), digits = 3),
         min = round(min(values, na.rm = TRUE), digits = 3),
         std = round(sd(values, na.rm = TRUE), digits = 3),
         q25 = round(quantile(values, probs = .25,na.rm = TRUE), digits = 3),
         q75 = round(quantile(values, probs = .75,na.rm = TRUE), digits = 3),
         iqr = round(IQR(values,na.rm = TRUE), digits = 3),
         spread = round(max(values, na.rm = TRUE)-min(values, na.rm = TRUE), digits = 3),
         skewness = round(skewness(values, na.rm = TRUE), digits = 3)),
  caption = "Table 4: Main statistics parameters of AFU (night-time)", 
  align = c('l', rep('c', times = 10)))|>
  kableExtra::kable_classic_2(full_width = T)
```
