---
title: "R Notebook"
output:
  html_document:
    toc: yes
    toc_float: yes
    number_sections: yes
  '': default
editor_options:
  markdown:
    wrap: 75
---

Course: Field Course Micrometeorology and Urban Climate at the University
of Bern (Institute of Geography)

Supervisor: Prof. Dr. Stefan Brönnimann

Adviser: Dr. Moritz Gubler

Do you have questions about the workflow? Contact the Authors:

Bigler Patrick
([patrick.bigler1\@students.unibe.ch](mailto:patrick.bigler1@students.unibe.ch){.email})

Sarah Ogi
([sarah.ogi\@students.unibe.ch](mailto:sarah.ogi@students.unibe.ch){.email})

Markella Bouchoriku
([markella.bouchoriku\@students.unibe.ch](mailto:markella.bouchoriku@students.unibe.ch){.email}
)

Reference: Zollikofen

# Introduction

|              |                     |
|--------------|---------------------|
| Coordinates: | 7°28' E, 46°59' N   |
| Altitude:    | 552 a.s.l.          |
| Time:        | UTC / GMT           |
| Source:      | Meteo Schweiz       |

: Table 1: Metadata for the MeteoSchweiz station in Zollikofen (reference
station)

|              |                                          |
|--------------|------------------------------------------|
| Coordinates: | 7° 27' 45,252'' E ; 46.° 57' 47,196'' N  |
| Altitude:    | 554.5 a.s.l.                             |
| Time:        | UTC-2 / GMT-2                            |
| Source:      | AFU (Amt für Umwelt der Stadt Bern)      |

: Table 2: Metadata for the MeteoSchweiz station in Zollikofen (reference
station)

+----------------+-----------------------------------------+
| Altitude:      | 7° 27' 50,65'' E ; 46.° 59' 26,844'' N  |
+----------------+-----------------------------------------+
| Altitude:      | 552.9 a.s.l.                            |
+----------------+-----------------------------------------+
| Time format:   | Old logger: UTC-2 / GMT-2               |
|                |                                         |
|                | New Logger: UTC / GMT                   |
+----------------+-----------------------------------------+
| Logger Number: | 98                                      |
+----------------+-----------------------------------------+
| Code grafana   | 20d1b9040ad9                            |
+----------------+-----------------------------------------+

: Table 3: Metadata for the 2m Logger in Zollikofen

+----------------+------------------------------------------+
| Altitude:      | 7° 27' 45,252'' E ; 46.° 57' 47,196'' N  |
+----------------+------------------------------------------+
| Altitude:      | 554.5 a.s.l.                             |
+----------------+------------------------------------------+
| Time format:   | Old logger: UTC-2 / GMT-2                |
|                |                                          |
|                | New Logger: UTC / GMT                    |
+----------------+------------------------------------------+
| Logger Number: | 83                                       |
+----------------+------------------------------------------+
| Code grafana   | d6e2769def35                             |
+----------------+------------------------------------------+

: Table 4: Metadata for the 2m Logger at AFU

# Preparation

```{r read_the_packages, warning=FALSE, error=FALSE, message=FALSE}
# install and activate all packages we need
source("../R/general/packages.R")

# We set preferences
conflicts_prefer(ggplot2::annotate)
conflicts_prefer(dplyr::select)
conflicts_prefer(dplyr::mutate)
conflicts_prefer(dplyr::filter)
conflicts_prefer(dplyr::rename)
```

```{r read_the_data, warning=FALSE, error=FALSE, message=FALSE}
# We read the reference data from Zollikofen
ZOLL <- read.csv2("../data/data_REF_ZOLL.original.csv")

# We read the reference data from AFU
AFU <- read_xlsx("../data/data_REF_AFU_new.xlsx")
```

```{r file-preparation}
# We change format of time and date for reference station in Zollikofen
ZOLL$time <- strptime(ZOLL$time, format="%Y%m%d%H%M")
ZOLL$time <- as.POSIXct(ZOLL$time, tz = "ETC/GMT")
attr(ZOLL$time, "tzone")

ZOLL <- ZOLL|>
  mutate('windspeed' = as.numeric(as.character(unlist(ZOLL[,'fu3010z0']))),
         'winddirection' = as.numeric(as.character(unlist(ZOLL[,'dkl010z0']))),
         'precipitation' = as.numeric(as.character(unlist(ZOLL[,'rre150z0']))),
         'humidity' = as.numeric(as.character(unlist(ZOLL[,'ure200s0']))),
         'insolation' = as.numeric(as.character(unlist(ZOLL[,'gre000z0']))),
         'temperature' = as.numeric(as.character(unlist(ZOLL[,'tre200s0']))))|>
  select(c('time', 'temperature', 'humidity', 'insolation', 'windspeed', 'winddirection'))

# We change format of time and date for reference station in front of AFU
AFU$Zeit <- format(AFU$Zeit, format = "%H:%M")
AFU$Datum <- strptime(paste(AFU$Datum,AFU$Zeit,sep = " "), format="%Y-%m-%d %H:%M") 
AFU$Datum <- as.POSIXct(AFU$Datum, tz = "Etc/GMT-2")
attr(AFU$Datum, "tzone")

AFU <- AFU|>
  rename('time' =  Datum,
         'temperature' = Temp,
         'windspeed' = WG,
         'winddirection' = WR...5,
         'insolation' = GS,
         'pressure' = Luftdruck,
         'humidity' = Feuchte)|>
  select(c('time', 'temperature', 'humidity', 'insolation', 'windspeed', 'winddirection'))
```

# Maschine Learning (KNN-Algorithm)

## General Zollikofen

```{r}
# We load our functions
source("../R/ml_functions.approach/knn.evaluation.approach.R")
source("../R/ml_functions.approach/lm.and.knn.model.approach.R")
source("../R/ml_functions.approach/knn_cv_optimizer.approach.R")
source("../R/ml_functions.approach/knn.cv.model.creater.approach.R")

set.seed(123)  

# Split 70 % to 30 % 
split_zoll_approach <- rsample::initial_split(ZOLL, prop = 0.7)
# We create a training set and a test set
ZOLL_train_approach <- rsample::training(split_zoll_approach)
ZOLL_test_approach <- rsample::testing(split_zoll_approach)

# We optimaze the hyperparameter k --> k=170
my.sequence <-c(1,2,3,4,5, seq(10, to = 50, by = 5))
parameter.extracter.knn.cv.a(my.sequence, ZOLL_train_approach, ZOLL_test_approach , 10)


# We calculate a KNN model
model.ZOLL.opt.appraoch <- knn.cv.model.a(ZOLL_train_approach, 2)

# We calculate a lm-model (to comapre with)
model.ZOLL.lm.approach <- lm.model.a(ZOLL_train_approach)

# Evaluation of the models
# KNN
eval_model.a(model.ZOLL.opt.appraoch, ZOLL_train_approach, ZOLL_test_approach, 
           c("Zollikofen KNN (opt. k = 2)"), c("Zollikofenn KNN (opt. k = 2)"))
# lm
eval_model.a(model.ZOLL.lm.approach, ZOLL_train_approach, ZOLL_test_approach, 
           c("Zollikofen with lm-model"), c("Zollikofen with lm-model"))

```

## General AFU

```{r}
set.seed(123)  

# Split 70 % to 30 % 
split_AFU_approach <- rsample::initial_split(AFU, prop = 0.7)
# We create a training set and a test set
AFU_train_approach <- rsample::training(split_AFU_approach)
AFU_test_approach <- rsample::testing(split_AFU_approach)

# We optimaze the hyperparameter k --> k=170
my.sequence <-c(1,2,3,4,5, seq(10, to = 50, by = 5))
parameter.extracter.knn.cv.a(my.sequence, AFU_train_approach, AFU_test_approach , 10)


# We calculate a KNN model
model.AFU.opt.appraoch <- knn.cv.model.a(AFU_train_approach, 5)

# We calculate a lm-model (to comapre with)
model.AFU.lm.approach <- lm.model.a(AFU_train_approach)

# Evaluation of the models
# KNN
eval_model.a(model.AFU.opt.appraoch, AFU_train_approach, AFU_test_approach, 
           c("Zollikofen KNN (opt. k = 2)"), c("Zollikofenn KNN (opt. k = 2)"))
# lm
eval_model.a(model.AFU.lm.approach, AFU_train_approach, AFU_test_approach, 
           c("Zollikofen with lm-model"), c("Zollikofen with lm-model"))
```

## Zollikofen

```{r knn-model-zollikofen}
# We load our functions
source("../R/ml_functions/knn.evaluation.R")
source("../R/ml_functions/lm.and.knn.model.R")
source("../R/ml_functions/knn_cv_optimizer.R")
source("../R/ml_functions/knn.cv.model.creater.R")

# For reproducibility (pseudo-random)
set.seed(123)  

# Split 70 % to 30 % 
split_zoll <- rsample::initial_split(ZOLL, prop = 0.7)
# We create a training set and a test set
ZOLL_train <- rsample::training(split_zoll)
ZOLL_test <- rsample::testing(split_zoll)

# We optimaze the hyperparameter k --> k=170
my.sequence <-c(1,2,3,4,5, seq(100, to = 200, by = 10))
parameter.extracter.knn.cv(my.sequence, ZOLL_train, ZOLL_test , 10)


# We calculate a KNN model
model.ZOLL.opt <- knn.cv.model(ZOLL_train, 170)

# We calculate a lm-model (to comapre with)
model.ZOLL.lm <- lm.model(ZOLL_train)

# Evaluation of the models
# KNN
eval_model(model.ZOLL.opt, ZOLL_train, ZOLL_test, 
           c("Zollikofen KNN (opt. k = 170)"), c("Zollikofenn KNN (opt. k = 170)"))
# lm
eval_model(model.ZOLL.lm, ZOLL_train, ZOLL_test, 
           c("Zollikofen with lm-model"), c("Zollikofen with lm-model"))
```

## AFU

We do it the same for AFU...

```{r}
# For reproducibility (pseudo-random)
set.seed(123)  
# Split 70 % to 30 % 
split_AFU <- rsample::initial_split(AFU, prop = 0.7)
# We create a training set and a test set
AFU_train <- rsample::training(split_AFU)
AFU_test <- rsample::testing(split_AFU)


my.sequence <-  c(1:25)
# We optimaze the hyperparameter k --> k=17
parameter.extracter.knn.cv(my.sequence, AFU_train, AFU_test , 10)

# We calculate a KNN model
model.AFU.opt <- knn.cv.model(AFU_train, 17)

# We calculate a lm-model (to comapre with)
model.AFU.lm <- lm.model(AFU_train)

# Evaluation of the models
# KNN
eval_model(model.AFU.opt, AFU_train, AFU_test, 
           c("Zollikofen KNN (opt. k = 170)"), c("Zollikofenn KNN (opt. k = 170)"))
# lm
eval_model(model.AFU.lm, AFU_train, AFU_test, 
           c("Zollikofen with lm-model"), c("Zollikofen with lm-model"))
```

# Estimate performance of the new loggers

```{r}






```
